Multi-Robot Probabilistic Mapping and Exploration

### 2018-06-23 Dissertation/Thesis/tex/pogm.tex
fixed algorithms

\vspace*{0.05\columnwidth}
\begin{algorithm}[H]
	Function: $P(\mathbf{r}_k|Z)=\text{InverseSensorModelRayByRay}(P(\mathbf{r}_k),Z)$\;
	% $\forall$ $l\in\braces{1,2,\ldots,n_{l}}$\;

	\For{$l=1,2,\ldots,n_{l}$}{
		Find $n_{r,l}$ cells from $m$ corresponding to $z_l$\;
		Initialize $\eta_l^{-1}=0$ and $P(\bar{\mathbf{r}}_{1:l,0})=1$\;
		\For{$k=1,2,\ldots,n_{r,l}$}{
			$P(\mathbf{r}_{1:l,k+}) = P(\bar{\mathbf{r}}_{1:l,0:k-1})P(\mathbf{r}_{1:l,k})$\;
			$P(\bar{\mathbf{r}}_{1:l,0:k})=P(\bar{\mathbf{r}}_{1:l,0:k-1})(1-P(\mathbf{r}_{1:l,k}))$\;
    			$a_\text{temp}=P(\mathbf{r}_{1:l,k+})p(z_l|\mathbf{r}_{1:l,k+},X)$\;
   			$\tilde P(\mathbf{r}_{l,k}|z_{1:l})=P(\mathbf{r}_{1:l,k})\eta^{-1}_{l}+a_\text{temp}$\;
   			$\eta_l^{-1}=\eta_l^{-1}+a_\text{temp}$\;
		}
	$\eta_l^{-1}=\eta_l^{-1}+P(\bar{\mathbf{r}}_{1:l,0:k})p(z_\text{max})$\;
	$P(\mathbf{r}_{k}|z_{1:l})=\eta\tilde P(\mathbf{r}_{k}|z_{1:l})$ for all $k\in\braces{1,2,\ldots,n_{r,l}}$\;
	Substitute $P(\mathbf{r}_{k}|z_{1:l})$ back into $P(m|z_{1:l})$\;
	}
	Return $P(m|Z)$\;
\caption{Inverse Sensor Model of an Individual Measurement Ray}
\label{alg:RayByRayISM}
\end{algorithm}
\vspace*{0.05\columnwidth}

@@

The synergistic scan inverse sensor model algorithm is summarized with the pseudocode of Algorithm \ref{alg:SynergisticScanISM} as a computationally efficient, recursive algorithm that avoids repeated calculations of the same quantity. This algorithm utilizes the following temporary variables to develop the algorithm in an efficient recursive form, defined as
\begin{align*}
a_k&=\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}\nonumber\\&\quad\times p(z_{t,l}|\mathbf{r}_{l,i},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1}),
\\
b_k&=\prod_{j=0}^{k-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1}),
\nonumber\\
c_k&=P(\bar{\mathbf{r}}_{l,k}|X_{1:t-1},Z_{1:t-1})^{-1}
\nonumber\\&\quad\times 
\sum_{i=k+1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}\nonumber\\&\quad\times p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1}),
\end{align*}
to compute \refeqn{ISM_Fusion}-\refeqn{xi}.

\begin{table}
\begin{tabular}{ l }
  for $l = 1,2,...,n_z$\\
   \ \ Obtain reduced map $r_{t,l}$\\
   \ \ Define $P(\mathbf{r}_{l,0}|X_{1:t-1},Z_{1:t-1})=0$, $P(\bar{\mathbf{r}}_{l,0}|X_{1:t-1},Z_{1:t-1})=1$, \\  \ \ \ \ \ \ \ \ \ \   $P(\mathbf{r}_{l,n_r+1}|X_{1:t-1},Z_{1:t-1})=1$;\\
   \ \ for $k = 1,2,...,n_r$\\
   \ \ \ \ Obtain $p(z_{t,l}|X_t,\mathbf{r}_{l,k})$ from a forward sensor model\\
   \ \ \ \ if $k=1$\\
   \ \ \ \ \ \ $a_1=0$, $b_1=1$;\\
   \ \ \ \ else\\
   \ \ \ \ \ \ $a_k=a_{k-1}+b_{k-1}p(z_{t,l}|\mathbf{r}_{l,k-1},X_t)P(\mathbf{r}_{l,k-1}|X_{1:t-1},Z_{1:t-1})$;\\
   \ \ \ \ \ \ $b_k=b_{k-1}P(\bar{\mathbf{r}}_{l,k-1}|X_{1:t-1},Z_{1:t-1})$;\\
   \ \ \ \ end if\\
   \ \ end for\\
   \ \ $c_{n_{r,l}+1}=0$;\\
   \ \ for $k = n_{r,l},n_{r,l}-1,...,1$\\
   \ \ \ \ $c_k=\frac{P(\mathbf{r}_{l,k+1}|X_{1:t-1},Z_{1:t-1})}{P(\bar{\mathbf{r}}_{l,k}|X_{1:t-1},Z_{1:t-1})}c_{k+1}$\\
   \ \ \ \ \ \ \ \ \ \ \ \ $+b_{k}p(z_{t,l}|\mathbf{r}_{l,k+1},X_t)P(\mathbf{r}_{l,k+1}|X_{1:t-1},Z_{1:t-1})$;\\
   \ \ end for\\
   \ \ for $k = 1,2,...,n_r$\\
   \ \ \ \ $\hat P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})=a_k+b_kp(z_{t,l}|\mathbf{r}_{l,k},X_t)$;\\
   \ \ \ \ $\hat P(\bar{\mathbf{r}}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})=a_k+c_k$;\\
   \ \ end for\\
   end for\\
   for all $i$ map cells inside the FOV\\
   \ \ Obtain the set $\mathcal L_i$ of $l_i$ measurement rays intersecting this cell\\
   \ \ if $l_i>0$\\
   \ \ \ \ $d=P(\mathbf{m}_i|X_{1:t-1},Z_{1:t-1})\prod_{\mathcal L_i}\hat P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})$;\\
   \ \ \ \ $e=P(\bar{\mathbf{m}}_i|X_{1:t-1},Z_{1:t-1})\prod_{\mathcal L_i}\hat P(\bar{\mathbf{r}}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})$;\\
   \ \ \ \ $P(\mathbf{m}_i|X_{1:t},Z_{1:t})=\frac{d}{d+e}$;\\
   \ \ else\\
   \ \ \ \ $P(\mathbf{m}_i|X_{1:t},Z_{1:t})=P(\mathbf{m}_i|X_{1:t-1},Z_{1:t-1});$\\
   \ \ end if\\
   \ \ Return: $P(\mathbf{m}_i|X_{1:t},Z_{1:t})$\\
   end for\\

\end{tabular}
\caption{Fast Algorithm of the Exact Solution of the Inverse Sensor Model for $l$ Simultaneous Measurement Rays}
\label{tab:Alg_ISM_2D}
\end{table}

>>>>

\vspace*{0.05\columnwidth}
\begin{algorithm}[H]
	Function: $P(m|X,Z)=\text{InverseSensorModelRayByRay}(P(m),X,Z)$\;
	% $\forall$ $l\in\braces{1,2,\ldots,n_{l}}$\;

	\For{$l=1,2,\ldots,n_{l}$}{
		Find $n_{r,l}$ cells from $m$ corresponding to $z_l$\;
		Initialize $\eta_l^{-1}=0$ and $P(\bar{\mathbf{r}}_{l,0}|X,z_{1:l-1})=1$ ($z_{1:0}$ is no condition)\;
		\For{$k=1,2,\ldots,n_{r,l}$}{
			$P(\mathbf{r}_{l,k+}|X,z_{1:l-1}) = P(\bar{\mathbf{r}}_{l,0:k-1}|X,z_{1:l-1})P(\mathbf{r}_{l,k}|X,z_{1:l-1})$\;
			$P(\bar{\mathbf{r}}_{l,0:k}|X,z_{1:l-1})=P(\bar{\mathbf{r}}_{l,0:k-1}|X,z_{1:l-1})(1-P(\mathbf{r}_{l,k}|X,z_{1:l-1}))$\;
    			$a_\text{temp}=P(\mathbf{r}_{l,k+}|X,z_{1:l-1})p(z_l|\mathbf{r}_{1:l,k+},X)$\;
   			$\tilde P(\mathbf{r}_{l,k}|X,z_{1:l})=P(\mathbf{r}_{l,k}|X,z_{1:l-1})\eta^{-1}_{l}+a_\text{temp}$\;
   			$\eta_l^{-1}=\eta_l^{-1}+a_\text{temp}$\;
		}
	$\eta_l^{-1}=\eta_l^{-1}+P(\bar{\mathbf{r}}_{l,0:k}|X,z_{1:l})p(z_\text{max})$\;
	$P(\mathbf{r}_{k}|z_{1:l})=\eta\tilde P(\mathbf{r}_{k}|X,z_{1:l})$ for all $k\in\braces{1,2,\ldots,n_{r,l}}$\;
	Substitute $P(\mathbf{r}_{k}|X,z_{1:l})$ back into $P(m|X,z_{1:l})$\;
	}
	Return $P(m|X,z_{1:n_{l}})=P(m|X,Z)$\;
\caption{Inverse Sensor Model of a Scan Updated Ray-By-Ray}
\label{alg:RayByRayISM}
\end{algorithm}
\vspace*{0.05\columnwidth}
\newpage

@@

The synergistic scan inverse sensor model algorithm is summarized with the pseudocode of Algorithm \ref{alg:SynergisticScanISM} as a computationally efficient, recursive algorithm that avoids repeated calculations of the same quantity. This algorithm utilizes the following temporary variables to develop the algorithm in an efficient recursive form, defined as
\begin{align*}
a_k&=\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}\nonumber\\&\quad\times p(z_{t,l}|\mathbf{r}_{l,i},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1}),
\\
b_k&=\prod_{j=0}^{k-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1}),
\nonumber\\
c_k&=P(\bar{\mathbf{r}}_{l,k}|X_{1:t-1},Z_{1:t-1})^{-1}
\nonumber\\&\quad\times 
\sum_{i=k+1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}\nonumber\\&\quad\times p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1}),
\end{align*}
to compute \refeqn{ISM_Fusion}-\refeqn{xi}. Once again, the history of poses and measurement scans are removed from the pseudocode for simplicity.

% TODO: check spacing of algorithms once complete
\vspace*{0.05\columnwidth}
\begin{algorithm}[H]
	Function: $P(m|X,Z)=\text{InverseSensorModelSynergistic}(P(m),X,Z)$\;
	\For{$l=1,2,\ldots,n_{l}$}{
		Find $n_{r,l}$ cells from $m$ corresponding to $z_l$\;
		Define $P(\mathbf{r}_{l,0})=0$, $P(\bar{\mathbf{r}}_{l,0})=1$, $P(\mathbf{r}_{l,n_{r,l}+1})=1$, and $c_{n_{r,l}+1}=0$\;
		\For{$k=1,2,\ldots,n_{r,l}$}{
			\If{$k=1$}{
				$a_1=0$, $b_1=1$\;
			}
			\Else{
				$a_k=a_{k-1}+b_{k-1}p(z_{l}|\mathbf{r}_{l,k-1},X)P(\mathbf{r}_{l,k-1})$, $b_k=b_{k-1}P(\bar{\mathbf{r}}_{l,k-1})$\;
			}
		}
		\For{$k = n_{r,l},n_{r,l}-1,...,1$}{
			$c_k=\frac{P(\mathbf{r}_{l,k+1})}{P(\bar{\mathbf{r}}_{l,k})}c_{k+1}+b_{k}p(z_{t,l}|\mathbf{r}_{l,k+1},X)P(\mathbf{r}_{l,k+1})$\;
		}
		\For{$k = 1,2,...,n_{r,l}$}{
			$\hat P(\mathbf{r}_{l,k}|z_{t,l},X)=a_k+b_kp(z_{t,l}|\mathbf{r}_{l,k},X)$, $\hat P(\bar{\mathbf{r}}_{l,k}|z_{t,l},X,)=a_k+c_k$\;
		}
	}
	\For{$i\in m_\text{FOV}$ \text{(map cells inside FOV)}}{
		Obtain the set $\mathcal L_i$ of $l_i$ measurement rays intersecting this cell\;
		\If{$l_i>0$}{
			$d=P(\mathbf{m}_i)\prod_{\mathcal L_i}\hat P(\mathbf{r}_{l,k}|z_{t,l},X)$\;
			$e=P(\bar{\mathbf{m}}_i)\prod_{\mathcal L_i}\hat P(\bar{\mathbf{r}}_{l,k}|z_{t,l},X)$\;
			$P(\mathbf{m}_i|X,Z)=\frac{d}{d+e}$\;
		}
		\Else{
			$P(\mathbf{m}_i|X,Z)=P(\mathbf{m}_i)$\;
		}
	}
	Return $P(m|X,Z)$\;
\caption{Inverse Sensor Model of a Scan Updated Synergistically}
\label{alg:SynergisticScanISM}
\end{algorithm}
\vspace*{0.05\columnwidth}
